Summary of tumor cell classification with `AUCell` for `r params$library_id`

### 2024-07-11 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-ewings")

>>>>

```{r base paths}
# The path to this module
module_base <- rprojroot::find_root(rprojroot::is_renv_project)
